EDA

### 2020-04-11 src/eda&modelling - 450/EDA&mode_fitting.Rmd

## Correlation for continuous variables
assess_class <- assessment_aggregate %>% ggplot(aes(x=assessTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and assess - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

tax_class <- assessment_aggregate %>% ggplot(aes(x=tax,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and tax - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

land_class<-assessment_aggregate %>% ggplot(aes(x=landTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and landTotal - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

improvementTotal_class<-assessment_aggregate %>% ggplot(aes(x=improvementTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and improvementTotal - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

land_class<-assessment_aggregate %>% ggplot(aes(x=landTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and landTotal - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

propertyCount_class<-assessment_aggregate %>% ggplot(aes(x=propertyCount,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and propertyCount - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

assess_class
tax_class
land_class
improvementTotal_class
propertyCount_class

@@

library(broom)
linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) 
```
Multiple R-squared:  0.8874,	Adjusted R-squared:  0.8707 
MSPE =  1.984285

@@

>>>>

## Correlation for continuous variables
assess_class <- assessment_aggregate %>% ggplot(aes(x=assessTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and assess - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
cor(assessment_aggregate$assessTotal, assessment_aggregate$rate)

tax_class <- assessment_aggregate %>% ggplot(aes(x=tax,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and tax - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
cor(assessment_aggregate$tax, assessment_aggregate$rate)

land_class<-assessment_aggregate %>% ggplot(aes(x=landTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and landTotal - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
cor(assessment_aggregate$landTotal, assessment_aggregate$rate)

improvementTotal_class<-assessment_aggregate %>% ggplot(aes(x=improvementTotal,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and improvementTotal - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
cor(assessment_aggregate$improvementTotal, assessment_aggregate$rate)

propertyCount_class<-assessment_aggregate %>% ggplot(aes(x=propertyCount,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_point() + ggtitle("mill rate and propertyCount - cor") + geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
cor(assessment_aggregate$propertyCount, assessment_aggregate$rate)

library(plotly)
ggplotly(assess_class)
ggplotly(tax_class)
ggplotly(land_class)
ggplotly(improvementTotal_class)
ggplotly(propertyCount_class)

@@

library(broom)

linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) 
```
Multiple R-squared:  0.8874,	Adjusted R-squared:  0.8707 
MSPE =  1.984285

@@

Summary on GOF
```{r}

GOF_table <- rbind(
      c("OLR full", 0.8874, 0.8707, 1.9843, 2.5902),
      c("OLR reduced", 0.8874, 0.8721, 1.9845, 2.5237),
      c("Ridge", 0.8868, 0.8707, 1.9896, 2.5675),
      c("LASSO", 0.8873, 0.8707, 1.9855, 2.5280),
      c("Elastic Net", 0.8625, 0.8707, 2.2366, 2.5486))
colnames(GOF_table) <- c("Model", "Mutiple R-Squared","Adjusted R_Squared", "MSE", "PMSE")
